\chapter*{Preface}
\label{ch:preface}
\addcontentsline{toc}{chapter}{\nameref{ch:preface}}

This thesis is on Morse theory,
the study of nice real valued functions on manifolds,
called Morse functions.
While elementary, they provide great insight in the structure of manifolds, eventually leading to some of the most important theorems in differential topology.
The goal of this thesis is to prove one of them, namely the generalized Poincaré conjecture in higher dimensions, stating that a homotopy sphere is a topological sphere.

This thesis could not have been written without the help of many people.

First and foremost, I would like to thank Dr.~Charlotte Kirchhoff-Lukat for proposing this subject and supervising me throughout my journey.
Charlotte, thank you for exposing me to the world of Morse theory and its many related topics.
Thank you for your advice, patience, and the weekly chats which kept me motivated through the year.

I would like to thank Prof.~Joeri Van der Veken and Dr.~François Thilmany for reading and evaluating this thesis.

I would like to thank my family for their support, giving me the opportunity to make this possible.

Lastly, Marie, thank you for the whiteboard in front of which we have spent many hours together.
It was essential for finishing this thesis.
Thank you for listening to my never ending rambles on Morse theory, proofreading my thesis, being the test subject for my presentations and for the much needed distraction.

\hfill \emph{Gilles, June 2021}
