\chapter*{TODO}
\begin{itemize}
    \item Relative Morse homology
    \item Historical aspects of Poincaré conjecture.
    \item Heegaard diagrams
    \item Introduce notion of perfect Morse function
\end{itemize}


TODOS at the end:
\begin{itemize}
    \item Check for uses of ascending / descending manifolds
    \item Think about what is a lemma, prop, theorem, \ldots (And also fix in text)
    \item Spell check in brackets
    \item Handle decompositions / handlebody / handle body
    \item Citation pages!
    \item Search for TODOs
    \item search for 'we get' and replace by something nicer
    \item Morse Capital letter
    \item Citations for every theorem
    \item Remove instances of won't, don't, let's, \ldots
    \item Check sidecite / sidenote after fullstop
    \item Captions should end with a full stop.
    \item Other sphere of `other' sphere or `other sphere' or ditch name? same for circle and other circle
    \item w.r.t. and i.e. spacing
        \item Fix notation for cardinality $|X| $ or  $\# X$.
        \item Search for 'quite' replace by something nicer
        \item no spaces before sidenote
        \item Bold math in backslash paragraphs
        \item Check for use of HM and H. Only use H after proof of morse = singular?
        \item pseudo-gradient vs pseudogradient
        \item map vs function
        \item etc etcetera et cetera
        \item additional paragraph summary: more motivation for more big picture, historic overview  to summary
        \item conclusion: suggestion, mayme mention floer cohomology business. Give an idea where you go ext.  again mention study that morse theory techniques a lot in 3-manifiold study (heegaard), 
        \item summary: good to include  why thesis, what does this add? nice pedagogie gel introduction bringing together lots of sources and providing graphic representations.
        \item 331
        \item copy shop tiensestraat?
        \item not any more -> no longer
        \item $h$-cobordism vs h-cobordism
        \item semicolon before field or ring in homology
\end{itemize}
